 Allocation scoring rules as a generalization of quantile scoring rules

### 2023-06-09 notes/allocation_notes.rmd
More work on entropy divergence reliability resolution and newsvendor

For notation, we will let
\begin{itemize}
\item $\mathcal{F_0}$ be the class of probability measures on the Borel-Lebesgue sets of $\mathbb{R}$
\item a probability measure $P \in \mathcal{F_0}$ induced by a random variable $X$ be identified by its cumulative distribution function $F_X$
\item $F$ denote the forecast distribution for the level of future need $Y$
\item $Y \sim G$
\item $Q_F := F^{-1}: [0,1] \rightrightarrows \mathbb{R}$ be the (set-valued) quantile function which maps a probability level $\alpha \in [0, 1]$ to the corresponding quantile set $\left[q_{\alpha, F}^{-}, q_{\alpha, F}^{+}\right]$ of $F$ where $q_{\alpha, F}^{-} := \sup \{x \mid F(x) < \alpha\}$ and 
$q_{\alpha, F}^{+} := \sup \{x \mid F(x) \leq \alpha\}$
\item $Q_\alpha: \mathcal{F_0} \rightrightarrows \mathbb{R}$ be the functional which maps a distribution $F$ to its $\alpha$-level quantile set
\item $q_{\alpha, F}$ be a (usually unique) element of $Q_F(\alpha) = Q_{\alpha}(F)$. 
\end{itemize}

We measure the forecaster's performance when the realized need is $y$ with the scoring function
\begin{align}
s(x,y)=s_{O,U}(x,y) &= O(g(x) - g(y))\sb{+} + U(g(y)-g(x))\sb{+} \label{eqn:scalar_score}
\end{align}
where $u_+ := u \mathbb{1}\{u > 0\}$ and $\mathbb{1}\{A\}$ is the indicator function of the event $A$. This is a \emph{negatively oriented} scoring function.
That is, a smaller score indicates better performance corresponding to a smaller cost due to under- or over-prediction of the realized $y$.

By making the forecaster aware of $s$ prior to prediction, we elicit an $\alpha$-level quantile $q_{\alpha,F}$ of the forecast distribution $F$ for $Y$, 
where $\alpha = U/(U+O)$. To see this, notice that if a forecaster believes that $Y \sim F$, they will calculate their expected score to be
\begin{align} 
\sbar_F(x) = E_F[s(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(Y) - g(x))\sb{+}]. \label{eqn:scalar_obj}
\end{align}
In order to minimize this expectation, they must forecast a solution of the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_F(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(Y) - g(x))\sb{+}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= (O+U) g^{\prime}(x)\left(F(x) - \alpha\right), \label{scalar_Z_deriv}
\end{align}
that is, a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$.
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x< \inf\left(Q_F\left(\alpha\right)\right)\}$ and non-negative on $\{x>\sup\left(Q_F\left(\alpha\right)\right)\}$.
 With the assumptions that $g^{\prime}(q)>0$ and that $Q_F\left(\alpha\right)$ is the singleton $\{q_{\alpha, F}\}$, this minimum is unique since
\begin{align}
\frac{d^2}{dx^2}\sbar_F(x)\big|_{x=q_{\alpha, F}} 
&= (O+U)\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
&= (O+U)(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}

@@

Note from \eqref{eqn:scalar_score_ident} that $\frac{d}{dx}\sbar_F(x) =\frac{d}{dx}E_F[s(x,Y)] = k(x)E_F[V(x,Y)]$, where $k(x) = \kappa g^{\prime}(x)$ and 
\begin{align}
V(x,y) 
% &\coloneq (1-\alpha)\mathbb{1}\{y < x\} - \alpha \mathbb{1}\{y \geq x\} \mathrel{\phantom{=}}\\
% &= (1-\alpha)\mathbb{1}\{y < x\} - \alpha \left(1 - \mathbb{1}\{y < x\}\right) \\
&= \mathbb{1}\{y \leq x\} - \alpha. 
\end{align}
By virtue of $E_F[V(Q_F(\alpha),Y)]=0$, $V$ is said to be an \emph{identification function} for the $\alpha$ quantile. The fact that, generally speaking, any elicitable functional (such as a quantile) has an identification function is known as \emph{Osband's principle}.

Forecasting the minimizer of $\sbar_F(x) = E_F[s_{\kappa,\alpha}(x,Y)]$ in this situation is known as the \emph{Bayes act} $a_F$ under $s_\alpha$ for the forecaster. Assuming a forecaster is informed, rational, and risk-neutral enough to take $a_F$, we can evaluate $F$, implicitly, as a distributional forecast, by the \emph{scoring rule} $S_{\alpha}$ induced by $s_{\alpha}$:
\begin{align}
S_{\alpha}(F,y) := s_{\alpha}(Q_F(\alpha), y).
\end{align}
If $y$ is generated by $Y \sim G$ then $S_{\alpha}(F,y)$ is an estimate of 
\begin{align}
S_{\alpha}(F,G) &:= E_G[S_{\alpha}(F,Y)] = E_G[s_{\alpha}(Q_{F}(\alpha),Y)].
\end{align}
The estimand here is the value at $G$ of the functional $\mathcal{\overline{S}}$ on $\mathcal{F_0}$ given by
\begin{align}
\mathcal{\overline{S}}_{G,\alpha}(F) := \sbar_G(Q_{\alpha}(F))
\end{align}
where $Q_{\alpha}$ is the $\alpha$ quantile functional. This is the expected value under $s$ of the forecaster's $\alpha$ quantile under the \emph{actual} data generating process $G$.

@@

Corresponding to the two expressions of an expectation $E_F[h(y)\mathbb{1}\{a < y<b\}]$ as either side of the Riemann-Stieltjes integration-by-parts 
formula $\int_{a}^{b}h(y)dF(y) = h(y)F(y) \big|_{a}^{b} - \int_{a}^{b}F(y)dh(y)$, the expected score \eqref{eqn:scalar_obj}
can be written as either
\begin{align}
\sbar_F(x) &= O \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{Y \leq u < x\}dg(u) dF(y) + U \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{x \leq u < Y\}dg(u) dF(y) \\
&= O \int_{\mathbb{R}} \mathbb{1}\{u < x\} F(u) dg(u) + U \int_{\mathbb{R}} \mathbb{1}\{u \geq x\} (1-F(u)) dg(u) \\
&= O \int_{-\infty}^x F(u) dg(u) + U \int_{x}^{\infty}(1-F(u)) dg(u), \label{eqn:scalar_obj_cdf_form} 
\end{align}
or
\begin{align}
\nonumber \sbar_F(x) &= O\int_{-\infty}^x(g(x) - g(y))dF(y) + U\int_x^{\infty}(g(y) - g(x))dF(y)\\ 
&= O\left(g(x)F(x) - \int_{-\infty}^x g(y)dF(y) \right) + U \left( \int_x^{\infty} g(y)dF(y) - g(x)(1-F(x))\right) \\
&= g(x)\left((O+U)F(x) - U\right) -  (O+U)\int_{-\infty}^x g(y)dF(y) + U \int_{\mathbb{R}} g(y)dF(y) \\
&= \kappa\left[g(x)(F(x) - \alpha) -\overline{g}_{F}(x) + \alpha \overline{g}\sb{F}\right] \label{eqn:obj_pexp} 
\end{align}
where 
\begin{align}
\overline{g}_F(x) &= E_{F}[g(Y)\mathbb{1}\{Y \leq x\}] \label{eqn:gbarx} \\
\overline{g}\sb{F} &= E_{F}[g(Y)]. \label{eqn:gbar}
\end{align}

@@

Taking, for example, $g(x)=x$ and $F = \mathrm{Exp}(1/\sigma)$, we have
\begin{align}
\overline{g}_{F}(x) = \int_{0}^{\max(0,x)} y \frac{e^{-y/\sigma}}{\sigma}dy = \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right]
\end{align}
so that \eqref{eqn:obj_pexp} is
\begin{align}
\sbar_{\mathrm{Exp}(1/\sigma)}(x) 
&= \kappa\left[x(\mathbb{1}\{x \geq 0\} \left[1 -e^{-x / \sigma}\right]  - \alpha) - \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right] + \alpha\sigma\right] \\
&= \kappa\left[\mathbb{1}\{x \geq 0\}\sigma e^{-x / \sigma} + (\mathbb{1}\{x \geq 0\} - \alpha)(x-\sigma)\right].
\end{align}

And if $F=F_{\mu, \sigma}$ lies in a location-scale family, that is, $F(x)= F_0\left(\frac{x-\mu}{\sigma}\right)$, we have
\begin{align}
\int_{-\infty}^{x} y dF(y) &= \int_{-\infty}^{\frac{x-\mu}{\sigma}}(\mu + \sigma z)dF_0(z) \\
& = \mu F(x) + \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z).
\end{align}
Then \eqref{eqn:obj_pexp} becomes
\begin{align}
\sbar_F(x) &= \kappa\left[x(F(x) - \alpha) - \mu F(x) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)  + \alpha E_F[Y]\right] \\
&= \kappa\left[F(x)(x-\mu) - \alpha(x - E_F[Y]) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)\right] \label{eqn:lc-form}
\end{align}

For example, if $F = U[a,b]$ is uniform we can take $F_0 = U[0,1], \mu = a, \sigma = b-a$, and \eqref{eqn:lc-form} is
\begin{align}
\sbar_F(x) &= 
\begin{cases}
-\alpha\kappa\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\kappa\left[\frac{x-a}{b-a}(x-a) -\alpha\left(x - \frac{a+b}{2}\right) -  (b-a) \frac{1}{2}\left(\frac{x-a}{b-a}\right)^2\right] & a < x < b \\[8pt]
\kappa\left[x - a -\alpha\left(x - \frac{a+b}{2}\right) - \frac{b-a}{2}\right] & b \leq x
\end{cases} \\
&=
\begin{cases}
-\kappa\alpha\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\frac{\kappa}{2}\left[\frac{1}{b-a}(x - (a+\alpha(b-a)))^2 +\alpha(1-\alpha)(b-a)\right] & a < x < b \\[8pt]
\kappa(1-\alpha)\left[ x - \frac{a+b}{2}\right] & b \leq x
\end{cases}
\end{align}

Thus, outside $(a,b)$, $\sbar_{U[a.b]}(x)$ has the form of pinball loss centered on the mean $m_F = \frac{a+b}{2}$ and is interpolated on $(a,b)$ 
 by a quadratic centered at the quantile $a+\alpha(b-a)$ with slopes matching the linear tails at $a$ and $b$ (see figure 1).

Or if $F=\Phi_{\mu,\sigma}$ is normal with location $\mu = E_F[Y]$ and scale $\sigma = \sqrt{\mathrm{Var}_F(Y)}$, 
we have 
\begin{align}
\int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)=-\frac{1}{\sqrt{2\pi}}\exp\left\{-\frac{(x-\mu)^2}{2 \sigma^2}\right\} = - \sigma\varphi_{\mu, \sigma}(x)
\end{align}
so that
\begin{align}
\sbar_F(x) = \kappa\left[(\Phi_{\mu,\sigma}(x) - \alpha)(x-\mu) + \sigma^2 \varphi_{\mu, \sigma}(x)\right].
\end{align}

@@

We finally note that for non-trivial $g$'s it may be helpful to make the substitution $v=g(u)$ in \eqref{eqn:scalar_obj_cdf_form} to get
\begin{align}
\sbar_F(x) &=  O \int_{-\infty}^{g(x)} F(g^{-1}(u)) du + U \int_{g(x)}^{\infty}(1-F(g^{-1}(u))) du
\end{align}
and in \eqref{eqn:gbarx} to get
\begin{align}
\overline{g}_F(x) &= \int_{-\infty}^{g(x)}v d(F \circ g^{-1})(v).
\end{align}

\subsection{Alternative Notation Possibilities}

Let $Y \sim F,F_i$ be various forecaster beliefs and $Y \sim G$ be reality.
\begin{align}
\overline{s}_{F,\kappa,\alpha}(x) &:= s_{\kappa,\alpha}(x,F) := E_F[s_{\kappa,\alpha}(x,Y)] \\
\overline{s}_{\kappa,\alpha}(x) &:= s_{\kappa,\alpha}(x,G) \\
s_{\symbfit{\kappa},\symbfit{\alpha}}(\mathbf{x}, \mathbf{F}) &:= 
\overline{s}_{\mathbf{F},\symbfit{\kappa},\symbfit{\alpha}}(\mathbf{x}) = 
\sum_{i}^{\mathrm{dim}\mathbf{x}} s_{\kappa_i,\alpha_i}(x_i, F_i) \\
S(F,y) &:= s(q_{F,\alpha}, y) \\
S(F_1,F_2) &:= E_{F_2}[S(F_1,Y)] = s(q_{F_1,\alpha}, F_2) \\
\overline{S}(F) &:= E_G[s(q_{F, \alpha}, Y)]
\end{align}

Define the $s$-entropy of an arbitrary $F$ 
\begin{align}
e_s(F) &:= E_F[S(F, Y)] = E_F[s(q_{F,\alpha}, Y)] = s(q_{F,\alpha}, F) \\
\end{align}
and of the RV $Y$ as
\begin{align}
e_s(Y) &:= e_s(G).
\end{align}
Define the $s$-divergence between two forecasts as
\begin{align}
d_s(F_1,F_2) &:= S(F_1,F_2) - S(F_2,F_2) = S(F_1,F_2) - e_s(F_2)
\end{align}
and the $s$-divergence from $F$ to $Y$ as
\begin{align}
d_s(F,Y) &:= S(F,G) - e(Y).
\end{align}

Thus, $\overline{S}(F) = d_s(F,Y) + e_s(Y)$.

>>>>

For notation, we will let
\begin{itemize}
\item $\mathcal{F_0}$ be the class of probability measures on the Borel-Lebesgue sets of $\mathbb{R}$
\item a probability measure $P \in \mathcal{F_0}$ induced by a random variable $X$ be identified by its cumulative distribution function $F_X$
\item $F$ denote some forecast distribution for the level of future need $Y$ which is known entirely or up to some parameters by its forecaster
\item $G$ denote the unknowable distribution of $Y$
\item $Q_F := F^{-1}: [0,1] \rightrightarrows \mathbb{R}$ be the (set-valued) quantile function which maps a probability level $\alpha \in [0, 1]$ to the corresponding quantile set $\left[q_{\alpha, F}^{-}, q_{\alpha, F}^{+}\right]$ of $F$ where $q_{\alpha, F}^{-} := \sup \{x \mid F(x) < \alpha\}$ and 
$q_{\alpha, F}^{+} := \sup \{x \mid F(x) \leq \alpha\}$
\item $Q_\alpha: \mathcal{F_0} \rightrightarrows \mathbb{R}$ be the functional which maps a distribution $F$ to its $\alpha$-level quantile set
\item $q_{\alpha, F}$ be a (usually unique) element of $Q_F(\alpha) = Q_{\alpha}(F)$
\item $q_{\alpha, Y}$ be an element of the unknowable set $Q_G(\alpha) = Q_{\alpha}(G)$
\end{itemize}

Let us measure the forecaster's performance when the realized need is $y$ with the scoring function
\begin{align}
s_{O,U}(x,y) &= O(g(x) - g(y))\sb{+} + U(g(y)-g(x))\sb{+} \label{eqn:scalar_score}
\end{align}
where $u_+ := u \mathbb{1}\{u > 0\}$ and $\mathbb{1}\{A\}$ is the indicator function of the event $A$. This is a \emph{negatively oriented} scoring function.
That is, a smaller score indicates better performance corresponding to a smaller cost due to under- or over-prediction of the realized $y$.

The scoring function $s_{O,U}$ has the special property that by giving the forecaster prior notice that $s_{O,U}$ will be used to measure performance, 
we \emph{elicit} an $\alpha$-level quantile $q_{\alpha,Y}$ for $Y$, 
where $\alpha = U/(U+O)$. That is, we create a situation where a forecaster believing that $Y \sim F$ and trying only to minimize their expected score 
\begin{align} 
\sbar_{F,O,U}(x) := E_F[s_{O,U}(x,Y)]  &= O E_F[(g(x) - g(Y))\sb{+}] + U E_F[(g(Y) - g(x))\sb{+}] \label{eqn:scalar_obj}
\end{align}
will report their quantile $q_{\alpha,F}$. To see this, notice that in order to minimize this expectation, they must forecast a solution of the first order equation
\begin{align}
\nonumber 0 =\frac{d}{dx}\sbar_{F,O,U}(x) 
&= O E_F\left[\frac{d}{dx}(g(x) - g(Y))\sb{+}\right] + U E_F\left[\frac{d}{dx}(g(Y) - g(x))\sb{+}\right] \\
&= O E_F[g^{\prime}(x)\mathbb{1}\{Y < x\}] + U E_F[-g^{\prime}(x)\mathbb{1}\{Y \geq x\}] \\
&= O g^{\prime}(x) \mathbb{P}_F(Y<x) - U g^{\prime}(x) \mathbb{P}_F(Y\geq x) \\
&= g^{\prime}(x)\left( O F(x) - U (1-F(x))\right) \\
&= (O+U) g^{\prime}(x)\left(F(x) - \alpha\right), \label{scalar_Z_deriv}
\end{align}
that is, a quantile $q_{\alpha, F} \in Q_F\left(\alpha\right)$.
(See \hyperref[scalar_Z_deriv_detail]{appendix} for an alternative derivation in terms of a density.)
The critical point $q_{\alpha, F}$ is actually a minimum since \eqref{scalar_Z_deriv} is non-positive on $\{x< \inf\left(Q_F\left(\alpha\right)\right)\}$ and non-negative on $\{x>\sup\left(Q_F\left(\alpha\right)\right)\}$.
 With the assumptions that $g^{\prime}(q)>0$ and that $Q_F\left(\alpha\right)$ is the singleton $\{q_{\alpha, F}\}$, this minimum is unique since
\begin{align}
\frac{d^2}{dx^2}\sbar_{F,O,U}(x)\big|_{x=q_{\alpha, F}} 
&= (O+U)\left(g^{\prime}(x)f(x) + g^{\prime \prime}(x)\left(F(x) - \alpha\right)\right)\big|_{x=q_{\alpha, F}} \label{scalar_Z_deriv2}\\
&= (O+U)(g^{\prime}(q_{\alpha, F})f(q_{\alpha, F}) + g^{\prime \prime}(q_{\alpha, F})\cdot 0) >0.
\end{align}

@@

Note from \eqref{eqn:scalar_score_ident} that $\frac{d}{dx}\sbar_{F,\alpha}(x) =\frac{d}{dx}E_F[s_{\alpha}(x,Y)] = k(x)E_F[V_{\alpha}(x,Y)]$, where $k(x) = \kappa g^{\prime}(x)$ and 
\begin{align}
V_{\alpha}(x,y) 
% &\coloneq (1-\alpha)\mathbb{1}\{y < x\} - \alpha \mathbb{1}\{y \geq x\} \mathrel{\phantom{=}}\\
% &= (1-\alpha)\mathbb{1}\{y < x\} - \alpha \left(1 - \mathbb{1}\{y < x\}\right) \\
&= \mathbb{1}\{y \leq x\} - \alpha. 
\end{align}
By virtue of $E_F[V_{\alpha}(Q_F(\alpha),Y)]=0$, $V_{\alpha}$ is said to be an \emph{identification function} for the $\alpha$ quantile. The fact that, generally speaking, any elicitable functional (such as a quantile) has an identification function is known as \emph{Osband's principle}.

Forecasting the minimizer of $\sbar_{F, \kappa,\alpha}(x) = E_F[s_{\kappa,\alpha}(x,Y)]$---that is, the forecaster quantile $q_{\alpha, F}$---is known as the \emph{Bayes act} $a_F$ under $s_\alpha$ for the forecaster. Assuming a forecaster is informed, rational, and risk-neutral enough to take $a_F$, we can evaluate $F$, implicitly, as a distributional forecast, by the \emph{scoring rule} $S_{\alpha}$ induced by $s_{\alpha}$
\begin{align}
S_{\alpha}(F,y) := s_{\alpha}(Q_F(\alpha), y).
\end{align}
It follows from this definition that
\begin{align}
S_{\alpha}(F,\tilde{F}) &:= E_{\tilde{F}}[S_{\alpha}(F,Y)] \geq S_{\alpha}(F,F) \quad\text{for all}\quad F, \tilde{F} \in  \mathcal{F_0}. \label{eq:properness}
\end{align}
A scoring rule $S(F,y)$ is said to be \emph{proper} when it satisfies \eqref{eq:properness} and \emph{strictly proper} when the inequality is strict.  $S_{\alpha}$ is not strictly proper since \eqref{eq:properness} is an equality for any $F$ and $\tilde{F}$ sharing an $\alpha$ quantile. $S_{\alpha}$ is however sometimes
said to be strictly proper for the $\alpha$ quantile since the inequality becomes strict whenever $q_{\alpha, F} \neq q_{\alpha, \tilde{F}}$, (see e.g., [@joseEvaluatingQuantileAssessments2009]). Another way to refer to this property is to call the scoring function $s_{\alpha}$ \emph{strictly consistent} for the 
$\alpha$ quantile functional [@gneitingMakingEvaluatingPoint2011]. Having a strictly consistent scoring function makes the $\alpha$ quantile \emph{elicitable}.

If $y$ is generated by $Y \sim G$ then $S_{\alpha}(F,y)$ is an estimate of 
\begin{align}
S_{\alpha}(F,G) &:= E_G[S_{\alpha}(F,Y)] = E_G[s_{\alpha}(Q_{F}(\alpha),Y)],
\end{align}
the expected value under $s_{\alpha}$ of the forecaster's $\alpha$ quantile under the \emph{actual} data generating process $G$.
More abstractly, this estimand is the value at $F$ of the functional $\mathcal{\overline{S}}_{G,\alpha}$ on $\mathcal{F_0}$ given by
\begin{align}
\mathcal{\overline{S}}_{G,\alpha}(F) := \sbar_{G,\alpha}(Q_{\alpha}(F))
\end{align}
where $Q_{\alpha}$ is the $\alpha$ quantile functional.

@@

Corresponding to the two expressions of an expectation $E_F[h(y)\mathbb{1}\{a < y<b\}]$ as either side of the Riemann-Stieltjes integration-by-parts 
formula $\int_{a}^{b}h(y)dF(y) = h(y)F(y) \big|_{a}^{b} - \int_{a}^{b}F(y)dh(y)$, the expected score \eqref{eqn:scalar_obj}
can be written as either
\begin{align}
\sbar_{F,O,U}(x) &= O \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{Y \leq u < x\}dg(u) dF(y) + U \int_{\mathbb{R}} \int_{\mathbb{R}} \mathbb{1}\{x \leq u < Y\}dg(u) dF(y) \\
&= O \int_{\mathbb{R}} \mathbb{1}\{u < x\} F(u) dg(u) + U \int_{\mathbb{R}} \mathbb{1}\{u \geq x\} (1-F(u)) dg(u) \\
&= O \int_{-\infty}^x F(u) dg(u) + U \int_{x}^{\infty}(1-F(u)) dg(u), \label{eqn:scalar_obj_cdf_form} 
\end{align}
or
\begin{align}
\nonumber \sbar_{F,O,U}(x) &= O\int_{-\infty}^x(g(x) - g(y))dF(y) + U\int_x^{\infty}(g(y) - g(x))dF(y)\\ 
&= O\left(g(x)F(x) - \int_{-\infty}^x g(y)dF(y) \right) + U \left( \int_x^{\infty} g(y)dF(y) - g(x)(1-F(x))\right) \\
&= g(x)\left((O+U)F(x) - U\right) -  (O+U)\int_{-\infty}^x g(y)dF(y) + U \int_{\mathbb{R}} g(y)dF(y) \\
&= \kappa\left[g(x)(F(x) - \alpha) -\overline{g}_{F}(x) + \alpha \overline{g}\sb{F}\right] \label{eqn:obj_pexp} 
\end{align}
where 
\begin{align}
\overline{g}_F(x) &= E_{F}[g(Y)\mathbb{1}\{Y \leq x\}] \label{eqn:gbarx} \\
\overline{g}\sb{F} &= E_{F}[g(Y)]. \label{eqn:gbar}
\end{align}

@@

Taking, for example, $g(x)=x$ and $F = \mathrm{Exp}(1/\sigma)$, we have
\begin{align}
\overline{g}_{F}(x) = \int_{0}^{\max(0,x)} y \frac{e^{-y/\sigma}}{\sigma}dy = \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right]
\end{align}
so that \eqref{eqn:obj_pexp} is
\begin{align}
\sbar_{\mathrm{Exp}(1/\sigma), \kappa, \alpha}(x) 
&= \kappa\left[x(\mathbb{1}\{x \geq 0\} \left[1 -e^{-x / \sigma}\right]  - \alpha) - \mathbb{1}\{x \geq 0\} \left[\sigma-e^{-x / \sigma}(\sigma+x)\right] + \alpha\sigma\right] \\
&= \kappa\left[\mathbb{1}\{x \geq 0\}\sigma e^{-x / \sigma} + (\mathbb{1}\{x \geq 0\} - \alpha)(x-\sigma)\right].
\end{align}

And if $F=F_{\mu, \sigma}$ lies in a location-scale family, that is, $F(x)= F_0\left(\frac{x-\mu}{\sigma}\right)$, we have
\begin{align}
\int_{-\infty}^{x} y dF(y) &= \int_{-\infty}^{\frac{x-\mu}{\sigma}}(\mu + \sigma z)dF_0(z) \\
& = \mu F(x) + \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z).
\end{align}
Then \eqref{eqn:obj_pexp} becomes
\begin{align}
\sbar_{F,\kappa,\alpha}(x) &= \kappa\left[x(F(x) - \alpha) - \mu F(x) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)  + \alpha E_F[Y]\right] \\
&= \kappa\left[F(x)(x-\mu) - \alpha(x - E_F[Y]) - \sigma \int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)\right] \label{eqn:lc-form}
\end{align}

For example, if $F = U[a,b]$ is uniform we can take $F_0 = U[0,1], \mu = a, \sigma = b-a$, and \eqref{eqn:lc-form} is
\begin{align}
\sbar_{F, \kappa,\alpha}(x) &= 
\begin{cases}
-\alpha\kappa\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\kappa\left[\frac{x-a}{b-a}(x-a) -\alpha\left(x - \frac{a+b}{2}\right) -  (b-a) \frac{1}{2}\left(\frac{x-a}{b-a}\right)^2\right] & a < x < b \\[8pt]
\kappa\left[x - a -\alpha\left(x - \frac{a+b}{2}\right) - \frac{b-a}{2}\right] & b \leq x
\end{cases} \\
&=
\begin{cases}
-\kappa\alpha\left[x - \frac{a+b}{2}\right] & x\leq a \\[8pt]
\frac{\kappa}{2}\left[\frac{1}{b-a}(x - (a+\alpha(b-a)))^2 +\alpha(1-\alpha)(b-a)\right] & a < x < b \\[8pt]
\kappa(1-\alpha)\left[ x - \frac{a+b}{2}\right] & b \leq x
\end{cases}
\end{align}

Thus, outside $(a,b)$, $\sbar_{U[a.b],\kappa,\alpha}(x)$ has the form of pinball loss centered on the mean $m_F = \frac{a+b}{2}$ and is interpolated on $(a,b)$ 
 by a quadratic centered at the quantile $a+\alpha(b-a)$ with slopes matching the linear tails at $a$ and $b$ (see figure 1).

Or if $F=\Phi_{\mu,\sigma}$ is normal with location $\mu = E_F[Y]$ and scale $\sigma = \sqrt{\mathrm{Var}_F(Y)}$, 
we have 
\begin{align}
\int_{-\infty}^{\frac{x-\mu}{\sigma}}zdF_0(z)=-\frac{1}{\sqrt{2\pi}}\exp\left\{-\frac{(x-\mu)^2}{2 \sigma^2}\right\} = - \sigma\varphi_{\mu, \sigma}(x)
\end{align}
so that
\begin{align}
\sbar_{F,\kappa,\alpha}(x) = \kappa\left[(\Phi_{\mu,\sigma}(x) - \alpha)(x-\mu) + \sigma^2 \varphi_{\mu, \sigma}(x)\right].
\end{align}

@@

We finally note that for non-trivial $g$'s it may be helpful to make the substitution $v=g(u)$ in \eqref{eqn:scalar_obj_cdf_form} to get
\begin{align}
\sbar_{F,O,U}(x) &=  O \int_{-\infty}^{g(x)} F(g^{-1}(u)) du + U \int_{g(x)}^{\infty}(1-F(g^{-1}(u))) du
\end{align}
and in \eqref{eqn:gbarx} to get
\begin{align}
\overline{g}_F(x) &= \int_{-\infty}^{g(x)}v d(F \circ g^{-1})(v).
\end{align}

\subsection{Entropy and Divergence}

Let $F,F_i$ be general distributions such as forecaster beliefs or reports about $Y$, and $G$ be the true distribution of $Y$. 
For a general scoring rule $S$, the $S$-entropy of $F$ is defined as 
\begin{align}
e_S(F) &:= S(F, F) = E_F[S(F, Y)].
\end{align}
Applying this to $S_\alpha$, we can define the $g,\alpha$-entropy of $F$ as
\begin{align}
e_{\alpha}(F) &:= S_{\alpha}(F, F) = E_F[s_{\alpha}(q_{F,\alpha}, Y)] .
\end{align}
If a forecaster believes that $Y \sim F$ then they expect to receive a score of $e_{\alpha}(F)$ by reporting their $\alpha$ quantile.
According to \eqref{eqn:scalar_obj_cdf_form} and \eqref{eqn:obj_pexp},
\begin{align}
e_{\alpha}(F)
&= (1-\alpha) \int_{-\infty}^{q_{\alpha,F}} F(u) dg(u) + \alpha \int_{{q_{\alpha,F}}}^{\infty}(1-F(u)) dg(u) \\
&= \alpha \overline{g}\sb{F}-\overline{g}_{F}(x).
\end{align}
Similarly, we define the $g,\alpha$-divergence between two distributions as
\begin{align}
d_{\alpha}(F_1,F_2) &:= S_{\alpha}(F_1,F_2) - S_{\alpha}(F_2,F_2) = S_{\alpha}(F_1,F_2) - e_{\alpha}(F_2). \label{egn:divergence}
\end{align}
Again from \eqref{eqn:scalar_obj_cdf_form} we get
\begin{align}
d_{\alpha}(F_1,F_2)
&= (1-\alpha) \int_{-\infty}^{q_{\alpha,F_1}} F_2(u) dg(u) + \alpha \int_{{q_{\alpha,F_1}}}^{\infty}(1-F_2(u)) dg(u) \\
&-(1-\alpha) \int_{-\infty}^{q_{\alpha,F_2}} F_2(u) dg(u) - \alpha \int_{{q_{\alpha,F_2}}}^{\infty}(1-F_2(u)) dg(u) \\
&= (1-\alpha) \int_{q_{\alpha,F_2}}^{q_{\alpha,F_1}} F_2(u) dg(u) + \alpha \int_{{q_{\alpha,F_1}}}^{q_{\alpha,F_2}}(1-F_2(u)) dg(u).
\end{align}
And from \eqref{eqn:obj_pexp},
\begin{align}
d_{\alpha}(F_1,F_2) &= g(q_{\alpha,F_1})(F_2(q_{\alpha,F_1}) - \alpha) -\overline{g}_{F_2}(q_{\alpha,F_1}) + \alpha \overline{g}\sb{F_2}  - \alpha \overline{g}\sb{F_2} + \overline{g}_{F_2}(q_{\alpha,F_2}) \\
&= g(q_{\alpha,F_1})(F_2(q_{\alpha,F_1}) - \alpha) + \int_{q_{\alpha,F_1}}^{q_{\alpha,F_2}}g(y)dF_2(y)
\end{align}
To emphasize the reality of $G$ we write $e_{\alpha}(G)$ as $e_{\alpha}(Y)$, which with \eqref{egn:divergence}
gives 
\begin{align}
S_{\alpha}(F,G) = d_{\alpha}(F,G) + e_{\alpha}(Y). \label{eqn:marg_score_decomp}
\end{align}
This expresses the true expected score of $F$ 
(i.e., not that calculated by the forecaster) as the sum of the failure of $F$ to match $G$ and the inherent uncertainty of $Y$.

We can also replace $G$ in \eqref{eqn:marg_score_decomp} by $G|F$, the true distribution of $Y$ \emph{given} that the forecaster 
believes $Y \sim F$---a belief presumably based on some knowledge of leading indicators for $Y$. This gives
\begin{align}
S_{\alpha}(F,G|F) &= d_{\alpha}(F,G|F) + e_{\alpha}(Y|F)
\end{align}
Using
\begin{align}
d_{\alpha}(G,G|F) = S_{\alpha}(G,G|F) - e_{\alpha}(Y|F)
\end{align}
this can be expanded to
\begin{align}
S_{\alpha}(F,G|F) &= d_{\alpha}(F,G|F) - d_{\alpha}(G,G|F) + S_{\alpha}(G,G|F). \label{eqn:cond_score_decomp}
\end{align}
Now view $F$ explicitly as a realization of a distribution-valued random variable $\mathcal{F}$ associated with the forecaster. 
To measure the forecaster's perfomance in general and not just on the occasion when they form 
the belief $Y\sim F$, we can take the $\mathcal{F}$ expectation of \eqref{eqn:cond_score_decomp} to get a decomposition
\begin{align}
E_{\mathcal{F}} [S_{\alpha}(F,G|F)] &= E_{\mathcal{F}} [d_{\alpha}(F,G|F)] - E_{\mathcal{F}}[d_{\alpha}(G,G|F)] + e_{\alpha}(Y).
\end{align}
The first two terms on the RHS are known as the \emph{unreliability} and the \emph{resolution} of the forecaster.
